\chapter{Appendices}
This chapter contains any and all important resources related to the project, such as the source code, 

\section{Source code}
The source code for this project is located on GitHub, at https://github.com/kevinniland97/Applied-Project-and-Minor-Dissertation. The repository contains the following main directories and files:

\begin{itemize}
    \item backend - Directory containing the code for the Flask Server.
    \item dissertation - Contains files for the dissertation.
    \item public - The public folder contains the HTML file for tweaking minor aspects of the application, such as the title.
    \item src - Contains all code used to develop the application.
\end{itemize}

\section{Installation and Usage}
Instructions on how to download, install and/or access this application can be found in the README.md of the GitHub repository. The README also contains a video that gives an overview of the repository and the project itself. The video can be found here: https://youtu.be/2GvhoUd2-po

\newpage
\section{Hosting}
This project is hosted using Firebase Hosting and the project is also Dockerized.

\subsection{Web Application}
The application can be found at the following link: https://algorithms-visualiser-react.firebaseapp.com. This version of the application was deployed using Firebase Hosting.

\medskip
The application is also dockerized and can also be found at localhost:3000, when run with Docker.

\subsection{Flask Server}
The Flask server used for user authentication can be found here: http://kniland97.eu.pythonanywhere.com.